---
title: "MSstatsPTM Simulation Analysis"
author: "Devon Kohler"
date: "7/14/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages}
library(MSstatsPTM)
library(data.table)
library(tidyverse)
```


```{r function, include=FALSE}

## Define metrics
calculate_summary_stats <- function(df, protein_col_name, pval_col_name, sd, rep, conditions){
  fpr <- df %>% filter(get(pval_col_name) < .05 & grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(get(pval_col_name) < .05))
  sensitivity <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(!grepl("NoChange", get(protein_col_name))))
  specificity <- df %>% filter(get(pval_col_name) >= .05 & grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(grepl("NoChange", get(protein_col_name))))
  precision <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / nrow(df %>% filter(get(pval_col_name) < .05))
  accuracy <- df %>% filter((get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) | 
                              (get(pval_col_name) >= .05 & grepl("NoChange", get(protein_col_name)))) %>% 
    nrow() / nrow(df)
  recall <- df %>% filter(get(pval_col_name) < .05 & !grepl("NoChange", get(protein_col_name))) %>% 
    nrow() / df %>% filter(!grepl("NoChange", get(protein_col_name))) %>% nrow()
  results_temp <- data.table(fpr = fpr, sensitivity = sensitivity, 
                             specificity = specificity, precision = precision, 
                             sd = sd, rep = rep, conditions = conditions,
                             accuracy = accuracy, recall = recall)
  return(results_temp)
}

```

## Computer Simulation

### Simulation Methods

To simulate data the `PTMsimulateExperiment()` function was used. This function allows us to vary the number of conditions, replicates, number of proteins, number of sites per protein, number of spectral features per site/protein, mean log2-abundance of PTM and PROTEIN, deviation from the mean log2-abundance in each group, standard deviation among replicates, and standard deviation among log2-intensities.

Three different statistical modeling methods were applied to the simulated data: MSstatsPTM, limma, and anova. These methods were tested both with and without applying protein level adjustment. MSstatsPTM uses TMP for summarization and post modeling calculations for the adjustment. To adjust limma and anova, the run-level data was averaged for both ptm and protein datasets and then combined. The resulting dataset was then used for limma and anova.

Graphs can help us visualize the components of the simulation.

```{r, echo=FALSE}
data.frame(ConditionA = rnorm(1000000, 22,2), ConditionB = rnorm(1000000, 17,2)) %>% ggplot() + 
  geom_density(aes(ConditionA), fill = "coral1") + geom_density(aes(ConditionB), fill = "steelblue1") +
  geom_vline(aes(xintercept=24), size = 1.25, color = "red") + 
  labs(title = "PTM1 between Condition A and B", x = "Abundance")
```


Here we can see a sample PTM with two conditions A and B. The red line represents a same biological replicate. We can simulate different variance's for the conditions.

**All charts are made using adjusted pvalue <.05 to designate a significant hit.**

### Simulation 1

All simulations were ran with half the PTMs being differential, while the other half the difference was due to changes in global protein level. The first simulation is run with the following parameters:

* Mean of log-intensity: $25$
* Number of Features: $10$ (PTM), $10$ (Protein)
* Standard deviations of log-intensities for modified and unmodified peptides: $0.2$, $0.3$
* Difference in PTM abundance between conditions: $0$, $1.$, $2.$, $2.$
* Difference in protein abundance between conditions: $0$, $0.5$
* Number of replicates: $2$, $3$, $5$, $10$
* Number of conditions: $2$, $3$, $4$
* Number of realizations: $1000$

``` {r first_sim_data, include = FALSE}

load(file = "../data/ptm_models_sim1.rda")#ptm_models_sim1
load(file = "../data/adjusted_models_sim1.rda")#adjusted_models_sim1 
load(file = "../data/anova_models_sim1.rda")#anova_sim1
load(file = "../data/adj_anova_models_sim1.rda")#adj_anova_sim1
load(file = "../data/limma_models_sim1.rda")#limma_results_sim1
load(file = "../data/adj_limma_models_sim1.rda")#adj_limma_sim1

s <- c(.2,.3)
reps <- c(2,3,5,10)
cond <- c(2,3,4)
param_combos <- expand.grid(s, reps, cond)

no_adj_results <- data.table()
adj_results <- data.table()
anova_results <- data.table()
anova_adj_results <- data.table()
limma_model_results <- data.table()
limma_adj_model_results <- data.table()

## Calculate results
## Calculate metrics for each model and dataset
for (i in seq_along(ptm_models_sim1)){
  
  no_adj_results_temp <- calculate_summary_stats(ptm_models_sim1[[i]], c("Protein"),  c("pvalue"), param_combos[i, 1], 
                                                 param_combos[i, 2], param_combos[i, 3])
  no_adj_results <- rbindlist(list(no_adj_results, no_adj_results_temp))
  
  adj_results_temp <- calculate_summary_stats(adjusted_models_sim1[[i]], c("Protein"),  c("adj.pvalue"), 
                                              param_combos[i, 1], param_combos[i, 2], param_combos[i, 3])
  adj_results <- rbindlist(list(adj_results, adj_results_temp))
  
  anova_results_temp <- calculate_summary_stats(anova_sim1[[i]], c("ptm"), c("pvalue"), param_combos[i, 1], 
                                              param_combos[i, 2], param_combos[i, 3])
  anova_results <- rbindlist(list(anova_results, anova_results_temp))
  
  temp <- adj_anova_sim1[[i]]
  temp_anova <- data.table()
  for (c in seq_along(unique(temp$label))){
    temp_anova <- rbindlist(list(temp_anova, 
                                 temp %>% filter(label == unique(temp$label)[c]) %>% 
                                   mutate(adj.pvalue = p.adjust(pvalue, method = "BH"))))
  }
  anova_adj_results_temp <- calculate_summary_stats(temp_anova, c("ptm"), c("adj.pvalue"), param_combos[i, 1], 
                                                param_combos[i, 2], param_combos[i, 3])
  anova_adj_results <- rbindlist(list(anova_adj_results, anova_adj_results_temp))
  
  limma_results_temp <- calculate_summary_stats(limma_results_sim1[[i]], c("PTM"), c("pvalue"), param_combos[i, 1], 
                                                    param_combos[i, 2], param_combos[i, 3])
  limma_model_results <- rbindlist(list(limma_model_results, limma_results_temp))
  
  temp <- adj_limma_sim1[[i]]
  temp_limma <- data.table()
  for (c in seq_along(unique(temp$Label))){
    temp_limma <- rbindlist(list(temp_limma, 
                                 temp %>% filter(Label == unique(temp$Label)[c]) %>% 
                                   mutate(adj.pvalue = p.adjust(pvalue, method = "BH"))))
  }
  
  limma_results_temp <- calculate_summary_stats(temp_limma, c("PTM"), c("adj.pvalue"), param_combos[i, 1], 
                                                param_combos[i, 2], param_combos[i, 3])
  limma_adj_model_results <- rbindlist(list(limma_adj_model_results, limma_results_temp))
}

## Label Models
adj_results$Model <- "MSstatsPTM"
adj_results$Color_Model <- "MSstatsPTM"
adj_results$Adj = TRUE
no_adj_results$Model <- "MSstats"
no_adj_results$Color_Model <- "MSstatsPTM"
no_adj_results$Adj = FALSE
anova_results$Model <- "basic ANOVA"
anova_results$Color_Model <- "ANOVA"
anova_results$Adj = FALSE
anova_adj_results$Model <- "ANOVA"
anova_adj_results$Color_Model <- "ANOVA"
anova_adj_results$Adj = TRUE
limma_model_results$Model <- "basic Limma"
limma_model_results$Color_Model <- "Limma"
limma_model_results$Adj = FALSE
limma_adj_model_results$Model <- "Limma"
limma_adj_model_results$Color_Model <- "Limma"
limma_adj_model_results$Adj = TRUE

## Combine to plot
models <- rbindlist(list(adj_results, no_adj_results, anova_results, 
                         anova_adj_results, limma_model_results, limma_adj_model_results), fill=TRUE)

cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")
cbPalette_first <- c("#56B4E9", "#E69F00", "#009E73", "#56B4E9", "#009E73", "#009E73", "#CC79A7", "#999999")
```

#### False Discovery Rate (FDR)

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 7, fig.height = 6}

models$plot_conditions = paste0(models$conditions, " Conditions")
models$plot_sd = paste0("SD ", models$sd)
models$Replicates = factor(models$rep)

png("../../MSstatsPTM-manuscript/main/images/sim1_FDR_all_models.png", width = 750, height = 500)
models %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "MSstats", "Limma", 
                                               "basic Limma", "ANOVA", "basic ANOVA")),
                  Color_Model = factor(Color_Model, levels=c("MSstatsPTM", "Limma", "ANOVA"))
                  ) %>%
  filter(conditions == 2 & sd == .2 & rep == 5) %>% 
  ggplot() + geom_col(aes(x = Model, y = fpr, fill = Color_Model, alpha = Adj)) + #, size = Replicates
  geom_hline(yintercept = .05, linetype = "dashed") + 
  scale_fill_manual(values=cbPalette) +
  scale_alpha_manual(values = c(.5, 1.0)) + 
  # scale_size_manual(values = c(3,5,7,9)) +
  # facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  # ylim(0.0, 0.4) + 
  guides(alpha = "none") + 
  guides(fill = "none") + 
  theme(axis.text.x = element_text(angle = 45, hjust=1, vjust = 1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=16),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 1: eFDR by Model", x = "Model", y = "FDR") + 
     guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))
dev.off()
```

``` {r, echo = FALSE, message=FALSE, warning=FALSE}

models$plot_conditions = paste0(models$conditions, " Conditions")
models$plot_sd = paste0("SD ", models$sd)

models %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "MSstats", "Limma", 
                                               "basic Limma", "ANOVA", "basic ANOVA")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("MSstatsPTM", "Anova", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = fpr, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  scale_size_manual(values = c(3,5,7,9)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 1: eFDR adjusted models", x = "Model", y = "FDR") + 
   guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))

```

When looking closer at the adjusted models only we can see that all the models we can see that they are indeed all very close to zero. The proposed solution has a slightly lower FDR than limma, while the anova has the lowest value. This may be because limma uses empirical bayes to lower the variance in the models, allowing more values to show as significant.

#### Recall (TPR)

Next we will look at the true positive rate, to see how the models perform when identifying differential ptms.

```{r echo=FALSE, message=FALSE, warning=FALSE}

models$plot_conditions = paste0(models$conditions, " Conditions")
models$plot_sd = paste0("SD ", models$sd)

models %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "MSstats", "Limma", 
                                               "basic Limma", "ANOVA", "basic ANOVA")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("MSstatsPTM", "Anova", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = recall, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  scale_size_manual(values = c(3,5,7,9)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 1: Recall adjusted models", x = "Model", y = "Recall") + 
   guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))
```

#### Accuracy

```{r echo=FALSE, message=FALSE, warning=FALSE}

models %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "MSstats", "Limma", 
                                               "basic Limma", "ANOVA", "basic ANOVA")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("MSstatsPTM", "Anova", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  scale_size_manual(values = c(3,5,7,9)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 1: Accuracy adjusted models", x = "Model", y = "Accuracy") + 
   guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))


```


``` {r, echo = FALSE, fig.width = 10, fig.height = 7}

conds <- c("G_2 vs G_1", "G_3 vs G_2", "G_4 vs G_3")
cond2 <- c("classG_1-classG_2",
"classG_2-classG_3",
"classG_3-classG_4")

boxplot_data <- data.table()
for (i in seq_len(nrow(param_combos))){
  temp1 <- adjusted_models_sim1[[i]] %>% filter(!grepl("NoChange", Protein) & Label %in% conds)
  temp1$Model <- "MSstatsPTM"
  temp2 <- adj_anova_sim1[[i]] %>% filter(!grepl("NoChange", ptm) & label %in% conds)
  temp2 <- setNames(temp2, c("ptm", "Label","log2FC", "SE", "tstat", "pval"))
  temp2$Model <- "ANOVA"
  temp3 <- adj_limma_sim1[[i]] %>% filter(!grepl("NoChange", PTM) & Label %in% cond2) 
  temp3 <- setNames(temp3, c('PTM', 'Label', 'log2FC', 'pvalue', 'df', 'se'))
  temp3$Model <- "Limma"

  temp <- rbindlist(list(temp1, temp2, temp3), fill = TRUE)
  temp$sd <- param_combos[i, 1]
  temp$reps <- param_combos[i, 2]
  temp$cond <- param_combos[i, 3]
  
  boxplot_data <- rbindlist(list(boxplot_data, temp))
}

boxplot_data$plot_conditions = paste0(boxplot_data$cond, " Conditions")
boxplot_data$plot_sd = paste0("SD ", boxplot_data$sd)

png("../../MSstatsPTM-manuscript/supplementary/sim_new/sim1_FC_boxplot.png", width = 750, height = 500)
boxplot_data %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "Limma", "ANOVA")),
                        reps = factor(reps, levels = c(2,3,5,10))) %>% 
  ggplot()  + geom_hline(yintercept = 1, color = "red", size = 1.1) + 
  geom_boxplot(aes(y = log2FC, x = reps, fill = Model)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  scale_fill_manual(values=cbPalette) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 1: Fold Change Distribution", x = "Replicates", y = "Log2FC")
dev.off()
```


### Simulation 2

In this simulation we introduce missing values and low replicates into the experiment. 20% of the features simulated were selected at random and masked with an NA value. No missing value imputation was used.

```{r, include=FALSE}

load(file = "../data/ptm_models_sim2.rda")#ptm_models_sim2
load(file = "../data/adjusted_models_sim2.rda")#adjusted_models_sim2
load(file = "../data/anova_models_sim2.rda")#anova_sim2
load(file = "../data/adj_anova_models_sim2.rda")#adj_anova_sim2
load(file = "../data/limma_models_sim2.rda")#limma_results_sim2
load(file = "../data/adj_limma_models_sim2.rda")#adj_limma_sim2

s <- c(.2,.3)
reps <- c(2,3,5,10)
cond <- c(2,3,4)
param_combos <- expand.grid(s, reps, cond)

no_adj_results <- data.table()
adj_results <- data.table()
anova_results <- data.table()
anova_adj_results <- data.table()
limma_model_results <- data.table()
limma_adj_model_results <- data.table()

## Calculate results
## Calculate metrics for each model and dataset
for (i in seq_along(ptm_models_sim2)){
  
  no_adj_results_temp <- calculate_summary_stats(ptm_models_sim2[[i]], c("Protein"),  c("pvalue"), param_combos[i, 1], 
                                                 param_combos[i, 2], param_combos[i, 3])
  no_adj_results <- rbindlist(list(no_adj_results, no_adj_results_temp))
  
  adj_results_temp <- calculate_summary_stats(adjusted_models_sim2[[i]], c("Protein"),  c("adj.pvalue"), 
                                              param_combos[i, 1], param_combos[i, 2], param_combos[i, 3])
  adj_results <- rbindlist(list(adj_results, adj_results_temp))
  
  anova_results_temp <- calculate_summary_stats(anova_sim2[[i]], c("ptm"), c("pvalue"), param_combos[i, 1], 
                                              param_combos[i, 2], param_combos[i, 3])
  anova_results <- rbindlist(list(anova_results, anova_results_temp))
  
  temp <- adj_anova_sim2[[i]]
  temp_anova <- data.table()
  for (c in seq_along(unique(temp$label))){
    temp_anova <- rbindlist(list(temp_anova, 
                                 temp %>% filter(label == unique(temp$label)[c]) %>% 
                                   mutate(adj.pvalue = p.adjust(pvalue, method = "BH"))))
  }
  anova_adj_results_temp <- calculate_summary_stats(temp_anova, c("ptm"), c("adj.pvalue"), param_combos[i, 1], 
                                                param_combos[i, 2], param_combos[i, 3])
  anova_adj_results <- rbindlist(list(anova_adj_results, anova_adj_results_temp))
  
  limma_results_temp <- calculate_summary_stats(limma_results_sim2[[i]], c("PTM"), c("pvalue"), param_combos[i, 1], 
                                                    param_combos[i, 2], param_combos[i, 3])
  limma_model_results <- rbindlist(list(limma_model_results, limma_results_temp))
  
  temp <- adj_limma_sim2[[i]]
  temp_limma <- data.table()
  for (c in seq_along(unique(temp$Label))){
    temp_limma <- rbindlist(list(temp_limma, 
                                 temp %>% filter(Label == unique(temp$Label)[c]) %>% 
                                   mutate(adj.pvalue = p.adjust(pvalue, method = "BH"))))
  }
  
  limma_results_temp <- calculate_summary_stats(temp_limma, c("PTM"), c("adj.pvalue"), param_combos[i, 1], 
                                                param_combos[i, 2], param_combos[i, 3])
  limma_adj_model_results <- rbindlist(list(limma_adj_model_results, limma_results_temp))
}

## Label Models
adj_results$Model <- "MSstatsPTM"
no_adj_results$Model <- "MSstatsPTM_no_adj"
anova_results$Model <- "anova_no_adj"
anova_adj_results$Model <- "ANOVA"
limma_model_results$Model <- "limma_no_adj"
limma_adj_model_results$Model <- "Limma"

## Combine to plot
models <- rbindlist(list(adj_results, no_adj_results, anova_results, 
                         anova_adj_results, limma_model_results, limma_adj_model_results), fill=TRUE)

```

#### Recall (TPR)

```{r echo=FALSE, message=FALSE, warning=FALSE}
models$plot_conditions = paste0(models$conditions, " Conditions")
models$plot_sd = paste0("SD ", models$sd)

models %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "MSstatsPTM_no_adj", "limma_no_adj", 
                                               "Limma", "anova_no_adj", "ANOVA")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("MSstatsPTM", "ANOVA", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = recall, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  scale_size_manual(values = c(3,5,7,9)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 2: Recall adjusted models", x = "Model", y = "Recall") + 
   guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))
```


#### Accuracy

```{r echo=FALSE, message=FALSE, warning=FALSE}
models %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "MSstatsPTM_no_adj", "limma_no_adj", 
                                               "Limma", "anova_no_adj", "ANOVA")),
                  Replicates = as.factor(rep)) %>%
  filter(Model %in% c("MSstatsPTM", "ANOVA", "Limma")) %>% 
  ggplot() + geom_point(aes(x = Model, y = accuracy, size = Replicates, color = Model)) + 
  scale_colour_manual(values=cbPalette) +
  scale_size_manual(values = c(3,5,7,9)) + 
  facet_grid(vars(plot_sd), vars(plot_conditions)) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust=1, size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
  labs(title = "Simulation 2: Accuracy adjusted models", x = "Model", y = "Accuracy") + 
   guides(color = guide_legend(order = 1, override.aes = list(size=5)), 
              size = guide_legend(order = 2, reverse = TRUE))
```


``` {r, echo = FALSE, fig.width = 10, fig.height = 7, message=FALSE, warning=FALSE}

conds <- c("G_2 vs G_1", "G_3 vs G_2", "G_4 vs G_3")
cond2 <- c("classG_1-classG_2",
"classG_2-classG_3",
"classG_3-classG_4")

boxplot_data <- data.table()
for (i in seq_len(nrow(param_combos))){
  temp1 <- adjusted_models_sim2[[i]] %>% filter(!grepl("NoChange", Protein) & Label %in% conds)
  temp1$Model <- "MSstatsPTM"
  # temp1$log2FC <- temp1$log2FC*-1
  temp2 <- adj_anova_sim2[[i]] %>% filter(!grepl("NoChange", ptm) & label %in% conds)
  temp2 <- setNames(temp2, c("ptm", "Label", "log2FC", "SE", "tstat", "pval"))
  temp2$Model <- "ANOVA"
  temp3 <- adj_limma_sim2[[i]] %>% filter(!grepl("NoChange", PTM) & Label %in% cond2) 
  temp3 <- setNames(temp3, c('PTM', 'Label', 'log2FC', 'pvalue', 'df', 'SE'))
  temp3$Model <- "Limma"
  # temp3$log2FC <- temp3$log2FC*-1
  
  temp <- rbindlist(list(temp1, temp2, temp3), fill = TRUE)
  temp$sd <- param_combos[i, 1]
  temp$reps <- param_combos[i, 2]
  temp$cond <- param_combos[i, 3]
  
  boxplot_data <- rbindlist(list(boxplot_data, temp))
}

boxplot_data$plot_conditions = paste0(boxplot_data$cond, " Conditions")
boxplot_data$plot_sd = paste0("SD ", boxplot_data$sd)

png("../../MSstatsPTM-manuscript/supplementary/sim_new/sim3_FC_boxplot.png", width = 750, height = 500)
boxplot_data %>% mutate(Model = factor(Model, levels=c("MSstatsPTM", "Limma", "ANOVA")),
                        reps = factor(reps, levels = c(2,3,5,10))) %>% 
ggplot()  + geom_hline(yintercept = 1, color = "red", size = 1.1) + 
geom_boxplot(aes(y = log2FC, x = reps, fill = Model)) + facet_grid(vars(sd), vars(cond)) + 
    scale_fill_manual(values=cbPalette) +
  theme_bw() +
  theme(axis.text.x = element_text(size = 16), 
         axis.text.y = element_text(size = 16), 
         legend.text=element_text(size=18),
         axis.title.y = element_text(size = 22),
         axis.title.x = element_text(size = 22),
         title = element_text(size = 22),
         strip.text = element_text(size = 16)) + 
labs(title = "Simulation 2: Fold Change Distribution", x = "Replicates", y = "Log2FC")
dev.off()

```

